---
title             : "Open Science: As Much About the Tools and Culture as Pre-Registration"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

# Introduction 

The way that educational researchers carry out their research has been a topic
of debate for a long time (cites). One topic that has been a part of this debate
concerns how open--to other researchers, stakeholders, to the public, and even
to participants--the research is (cites).

Some of the historical research has pin-pointed tensions around (cites):

  - privacy due to minors/the sensitive nature of the data
  - assymetries in terms of power between researchers and the teachers and
    students from whom data is collected
  - the need to protect data that was costly to collect

Recently, due to cultural and technical changes, these issues have been joined
by a focus on reproducibility. Reproducibility is an important consideration for
doing research that contributes to theory and builds our understanding of
educational practice. While reproducibility has been the focus of other
disciplines, where infrastructure and support for it are being developed,
educational research has been somewhat slow to embrace reproducible research.

While we agree that pre-registration as a way to achieve it is important, we believe that it is not the most important consideration in terms of meeting the aims of open science.

As [Leonelli argues](https://www.emeraldinsight.com/doi/abs/10.1108/S0743-41542018000036B009), reproducibility isn't the sole criterion for quality research. Scholars have made this point in the context of education, too (cite Hedges).

We argue that two things are at least as important as reproducibility, namely:

- The culture valueing openness
- Tools to make it possible and efficient to work in the open

# Past research on reproducibility (from our AERA workshop proposal and earlier drafts)

The basic premise of reproducible research is that quantitative analyses should
be conducted and documented with sufficient clarity that independent researchers
could reproduce all the results, exactly. Initially, this may sound relatively
straightforward---of course research findings should be reproducible---and we
may like to think that most research in education adheres to these principles.
Unfortunately, this is generally not the case. For example, in a large- scale
review of growth models published from 2007-2012 across 47 education and
psychology journals, @stevens13 found that documenting even relatively routine
procedures, such as how missing data were handled, was extraordinarily
difficult. Indeed, in the vast majority of cases, this information was simply
missing. 

These findings are congruent with @buckheit95, who argue "an article
about computational science in a scientific publication is **not** the
scholarship itself, it is merely the **advertising** of the scholarship. The
actual scholarship is the complete software development environment and the
complete set of instructions which generated the figures" (p. 5, emphasis in the
original). This may seem a somewhat extreme view, but it demonstrates that a
journal article on its own is generally insufficient for the accumulation of
scientific evidence. That is, it is difficult to build off the work of others,
or verify study results, if you only have access to the published findings. We
note that reproducibility does not imply "correctness", but rather a
transparency in process: In fact, part of the reason reproducible research is
essential is that it allows other researchers to verify the process and
analysis, and ultimately, the validity of the inferences made from a study.

Recent research about replication in particular (Gehlbach & Robinson, 2017). Research about building knowledge in the field, related to replication (Hedges, 2018).

Recent research about preparing educational researchers and advancing the methodological capabilities of the field (Henson, Hull, & Williams, 2010)

Recent calls for registered reports ([AERA Open](http://journals.sagepub.com/page/ero/collections/special-topic-collections/index), [Journal of Computer Assisted Learning](https://onlinelibrary.wiley.com/journal/13652729)).

# Past research on an open research culture

Societies emphasizing open science ([Society for the Improvement of Psychological Science](https://www.improvingpsych.org), [rOpenSci](https://ropensci.org/))

Past research on open science in general (Bertling  Friesike, 2014; National Research Council, 2018) and in educational research (Cook et al., pre-print publication;  McBee, Makel, Peters, & Matthews, pre-print publication; van der Zee & Reich, 2018) 

# Past research on open tools

Wickham? Python folks? Computational science folks?

# Three examples of an open culture and open tools leading to reproducible work

## Example 1: 

asf

## Example 2: 

sdf

## Example 3: 

sdf

# Key future directions

dfd

# Conclusions

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
